Visualization of [fulle name] Fractional Integrals

### 2019-04-11 fractional/CMJ style files/article-template.tex
added reason for why g is invertable
added a table of g and h
added a table frac integral
added h integral

\section{Geometric Interpretation of Fractional Integrals}

@@

@@

>>>>

\section{Geometric Interpretation of the Riemann-Liouville Fractional Integral}

@@

Note that $g_t^{\alpha}(\tau)$ is always invertable, since $\frac{d g_t^{\alpha}}{d \tau} = \frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)}>0$ for $\tau\in[0,t]$.

@@

By employing $h$ we can transform eq.~\ref{eq:cav} into the following Riemann integral:
\begin{equation}
\int_0^{\frac{t^{\alpha}}{\Gamma(\alpha+1)}} f\circ h_{\alpha}^t (\tau) d\tau.  
\end{equation}

\begin{table}[h!]
\centering
 \begin{tabular}{|c || c | c|} 
 \hline
 $\alpha$ & $g_{10}^{\alpha}(\tau)$ & $h_{10}^{\alpha}(\tau)$ \\ [0.5ex] 
 \hline\hline
 $0$ & 0 & $y=0$ \\ 
 $0.2$ & $[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-\tau}\right)$ & $10 - \left ( \sqrt[5]{10} -  \Gamma\left (\frac{6}{5} \right ) \tau \right )^5$  \\
 $0.4$ & $[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-\tau)^2}\right)$ & $10 - \sqrt{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{7}{5} \right ) \tau \right )^5}$ \\
 $0.6$ & $[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-\tau)^3}\right)$ & $10 - \sqrt[3]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{8}{5} \right ) \tau \right )^5}$ \\
 $0.8$ & $[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-\tau)^4}\right)$ & $10 - \sqrt[4]{\left ( \sqrt[5]{10} -  \Gamma\left (\frac{9}{5} \right ) \tau \right )^5}$ \\ [1ex] 
 $1$ & $\tau$ & $\tau$ \\ [1ex] 
 \hline
 \end{tabular}
\end{table}

\begin{table}[h!]
\centering
 \begin{tabular}{||c|| c| c||} 
 \hline
 $\alpha$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ & $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$ \\[0.5ex]
 \hline\hline
 \rule{0pt}{2.5ex}
 $0$ & $t$ & $\sqrt{t}$  \\  
 \rule{0pt}{2.5ex}
 $0.2$ & $\frac{25}{6\Gamma(\frac{1}{5})} t^{\frac{6}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{17}{10})} t^{\frac{7}{10}}$  \\ 
 \rule{0pt}{2.5ex}
 $0.4$ & $\frac{25}{14\Gamma(\frac{2}{5})} t^{\frac{7}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{19}{10})} t^{\frac{9}{10}}$  \\
 \rule{0pt}{2.5ex}
 $0.6$ & $\frac{25}{24\Gamma(\frac{3}{5})} t^{\frac{8}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{21}{10})} t^{\frac{11}{10}}$  \\ 
 \rule{0pt}{2.5ex}
 $0.8$ & $\frac{25}{36\Gamma(\frac{4}{5})} t^{\frac{9}{5}}$  & $\frac{\sqrt{\pi}}{2\Gamma(\frac{23}{10})} t^{\frac{13}{10}}$  \\ 
 \rule{0pt}{2.5ex}
 $1$ & $\frac{1}{2}t^2$  & $\frac{2}{3}t^{\frac{3}{2}}$  \\ [1ex]
 \hline
 \end{tabular}
\end{table}

\section{Examples}
We use the geometric framework we presented in the previous paragraph to provide 
To make things clear we provide two fully worked examples below of how to geometrically interpret fractional integrals using conversion  presented in the previsous 
section. The two fractional integrals we will visualize are:\\

\noindent
$\frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau$ and $\frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau$.\\

The steps to visualize the above two integral wer described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
Riemann-Stieltjes integrals are then converted to Cavalieri integrals. The graphical
